---
title: "Borough vs Violation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(data.table)
library(tidyverse)
library(patchwork)
library(plotly)
library(haven)
raw_data<-read_csv(file="./data/DOHMH_Childcare_Center_Inspections .csv")

Childcare_center<-
  raw_data%>%
  janitor::clean_names() %>%
  filter(status=="Permitted")%>%
  select(-legal_name,-building,-street,-phone,-permit_number,-permit_expiration,
         -day_care_id,-url,-date_permitted,-actual)%>%
  drop_na(violation_rate_percent)%>% ## change from 17356 to 15910
  drop_na(public_health_hazard_violation_rate) %>% ## actually no change
  filter(age_range != "0 YEARS - 16 YEARS")
```

### Borough vs. Inspection summary result 

We examined the inspection categories of child care centers in different areas of New York that had records of violations，We found that the categories of inspection are divided into four major categories, which are Compliance Inspection of Open Violations, Initial Annual Inspection, Lead Based Paint or Lead in Water Inspection, Monitoring Inspection Non-Routine.
```{r, warning=FALSE, message=FALSE}
borough_inspec_summmary<-
  Childcare_center%>%
  select(borough,inspection_summary_result)%>%
  drop_na(inspection_summary_result)%>%
  group_by(borough,inspection_summary_result)%>%
  summarise(
    n_obs=n()
  )%>%
  mutate(
    general_category=case_when(
      inspection_summary_result %like% "^Compliance Inspection of Open Violations" ~"Compliance Inspection of Open Violations",
      inspection_summary_result %like% "^Initial Annual Inspection" ~"Initial Annual Inspection",
      inspection_summary_result %like% "^Lead Based Paint or Lead in Water Inspection" ~"Lead Based Paint or Lead in Water Inspection",
      inspection_summary_result %like% "^Monitoring Inspection Non-Routine" ~"Monitoring Inspection Non-Routine")
  )
head(borough_inspec_summmary)
```

To better examine the number of violations in different types of inspections at child care centers in different borough of New York, we categorized and summarise the records of violation inspections by borough and type of inspection.

### Borough group by General Category
```{r, warning=FALSE, message=FALSE}
borough_inspec_general_sumary<-
  borough_inspec_summmary%>%
  group_by(borough,general_category)%>%
  summarise(
    n_obs=sum(n_obs)
  ) %>% 
  arrange(desc(n_obs))%>% 
  knitr::kable()
borough_inspec_general_sumary
```

We also created the following chart by type of inspection and the number of violations recorded. We found that New York's child care centers had the highest number of violations in the intial annual inspection, far exceeding the other three types of violations combined, with the Queen's district having the highest number of violations at 3,600 records. In contrast, Lead Based Paint or Lead in Water Inspection had the least number of violations, with bronx having ten records, Brooklyn having eleven records, Manhattan having six records, queens having five records, and staten island not even having this type of record.

```{r}
borough_inspec_general_sumary_plot_all<-
  borough_inspec_general_sumary%>%
  ggplot(aes(x=general_category,y=n_obs),)+
  geom_bar(aes(fill = borough), stat = "identity")+
  theme(axis.text.x = element_text(size=10, angle=45, hjust = 1))+
  labs(y="number of violations",title="Inspection categories vs. borough",x="inspection categories")
  
ggplotly(borough_inspec_general_sumary_plot_all)
```

### General Type vs Borough

```{r, warning=FALSE, message=FALSE}
inspec_general_borough_sumary<-
borough_inspec_summmary%>%
group_by(general_category,borough)%>%
summarise(
n_obs=sum(n_obs)
) %>% 
  arrange(desc(n_obs)) %>% 
  knitr::kable()
inspec_general_borough_sumary
```

The following chart can better understand the violation situation of different Boroughs in New York. We can see that queens has the most violation records, Brooklyn has less violation records than queens but still far more than bronx and Manhattan, and staten island has the least violation records.
```{r}
violation_borough_sumary_all<-
inspec_general_borough_sumary%>%
ggplot(aes(x=borough,y=n_obs))+
geom_bar(aes(fill=general_category),stat = "identity")+
theme(axis.text.x = element_text(size=10, angle=45, hjust = 1))+
  labs(y="number of violations",title="borough vs.Inspection categories",x="borough")
  
ggplotly(violation_borough_sumary_all)
```

# Borough vs Violation Category
```{r}
Childcare_center %>% 
  mutate(violation_category = ifelse(is.na(violation_category), "NO VIOLATION", violation_category)) %>% 
  group_by(borough, age_range) %>% 
  count(violation_category) %>% 
  ggplot(aes(fill =violation_category, x=borough,y = n))+
  geom_bar(position = "dodge", stat = "identity")
```

The graph above showing the relationship between the borough and the cases of violation in each category. From the grpah we can see, queens is the borough whihc has the most violation cases in all three categories and staten island has the least violation cases in all three categories. And in Brooklyn, it has the highest no violation cases. 

```{r, warning=FALSE, message=FALSE }
# try
try = Childcare_center %>% 
  mutate(violation_category = ifelse(is.na(violation_category), "NO VIOLATION", violation_category)) %>%
  select(borough,program_type,violation_category)%>%
  filter(program_type!="CAMP")%>%
  group_by(borough, program_type,violation_category) %>% 
  summarise(
    n_obs=n())%>%
  ggplot(aes(x = borough, y = n_obs, fill = violation_category))+
  geom_bar(stat="identity", width = 0.5, position = "dodge")+
  facet_grid(. ~ program_type) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 28),axis.text = element_text(size = 5))

ggplotly(try) 
```
The graph above is showing the relationship between borough and the number of violation category count in two different program types. The borough can separate the five parts "Bronx", "Brooklyn", "Manhattan", "Staten Island" and "Queens". Violation category can be separate "Critical", "General", "No Violation" and "Public Helath Hazard". Combining two graphs, pre school will have a higher violation cases in each borough in overall. In infant toddler, Brooklyn is the borough that having the largest violation cases.But in preschool, queens is the borough that having the largest cases. Staten island has the smallest cases in both preschool and infant toddler.