---
title: "map_Inspect_EDA"
author: "Shuting Kang"
date: "2022-12-09"
output: html_document
---

This markdown file is use for map and inspection EDA

step1: input dataset DOHMH Childcare Center Inspections (Updated from november 25,2022) from NYC OpenData 
```{r }
library(tidyverse)
library(ggridges)
raw_data<-read_csv(file="./data/DOHMH_Childcare_Center_Inspections .csv")
```
Due to irregularities in writing, there is a lot of duplication in the child care records. The same child care centers can be different in many separate records because of typo. We were interested in calculating the number of violations for each child care center more accurately, so we standardized the lowercase names of child care centers, removed punctuation and spaces, and eliminated characters that could cause inconsistencies to merge the same legal names. 
```{r}
children_center<-
  raw_data%>%
  janitor::clean_names()%>%
  mutate(
    legal_name=tolower(legal_name),
    legal_name=gsub('[[:punct:] ]+',' ',legal_name),
    legal_name=gsub(" ","",legal_name),
    legal_name=gsub("llc","",legal_name),
    legal_name=gsub("inc","",legal_name),
    legal_name=gsub("th","",legal_name),
    legal_name=gsub("school","",legal_name),
    legal_name=gsub("i","",legal_name),
    legal_name=gsub("center","",legal_name),
    legal_name=gsub("ctr","",legal_name)
  )%>%
  select(legal_name)%>%
  group_by(legal_name)%>%
  summarise(
    n_obs=n()
  )
```


We pinpointed the status of violation in different areas of New York's child care centers with zipcode, so the map can more visually present to the viewer the number of violations recorded in different areas of New York's child care centers.

```{r}
total_obs<-
  raw_data%>%
  janitor::clean_names()%>%
  drop_na(zip_code)%>%
  drop_na(violation_category)%>%
  select(zip_code,violation_category)%>%
  group_by(zip_code)%>%
  summarise(
    n_obs=n()
  )
total_obs
```

Map
```{r}
install.packages("rgdal")
install.packages("maps")
install.packages("BAMMtools")
install.packages("spdep")
install.packages("maptools")
library(tidyverse)
library(plotly)
library(rgdal)
library(plotly)
library(maps)
library(devtools)
library(leaflet)
library(BAMMtools)
library(spdep)
library(maptools)

zipcode<- read_csv("./US Zip Codes from 2013 Government Data.csv")
zipcode<-
  zipcode%>%
  mutate(
    zip_code=ZIP,
    zip_code=as.numeric(zip_code))

zipcode_lat<-
  left_join(total_obs,zipcode,by='zip_code')%>%
  mutate(
    zip_code=as.character(zip_code)
    )

# zip code tabulation area
# https://data.cityofnewyork.us/Business/Zip-Code-Boundaries/i8iw-xf4u/data
# import the shape file
# https://plotly-book.cpsievert.me/maps.html


zip_map <- readOGR(dsn = './data/ZIP_CODE_040114/ZIP_CODE_040114.shp', encoding = "UTF-8")

zip_map@data <- left_join(zip_map@data,zipcode_lat, by = c('ZIPCODE' = 'zip_code'))

# assign 0 for zip codes that have no match in the dog bite data
zip_map$n_obs[is.na(zip_map$n_obs)] <- 0

# CRS setting
zip_map_crs <- spTransform(zip_map, CRS("+init=epsg:4326"))
# export the json file
writeOGR(zip_map_crs, './data/zip_map_geojson', layer = 'zip_map', driver = 'GeoJSON')

# Layout 
# format of the label that pops up for each polygon
label_popup <- paste0(
  "<strong>Zip code: </strong>",
  zip_map$ZIPCODE,
  "<br><strong>Number of Violation: </strong>",
  zip_map$n_obs
)

# get jenks natural break for violation
getJenksBreaks(zip_map$n_obs, 6)
# set bins
bite_bins <- c(0, 25, 62, 97, 141, 260)
pit_bins <- c(0 , 4, 14, 25, 41, 80)
# set pals
bite_pal <- colorBin('Greens', bins = bite_bins, na.color = '#aaff56')

# choropleth map for violation
leaflet::leaflet(data = zip_map_crs) %>% 
  addProviderTiles('CartoDB.Positron') %>% 
  addPolygons(fillColor = ~bite_pal(n_obs),
              fillOpacity = 0.8,
              color = "#BDBDC3",
              weight = 1,
              popup = label_popup,
              highlightOptions = highlightOptions(color = "black", weight = 2,
      bringToFront = TRUE)) %>% 
  addLegend('bottomleft',
            pal = bite_pal,
            values = ~n_obs,
            title = 'Number of violation incidents by zip code',
            opacity = 1)
```


filter the variables to include currently permitted Children Care Center
Question: should we consider permitted (17356) or permitted+ active (3399)(school)

step1:filter the inspection record for only currently permitted Children Care Center
step2:remove the useless variables: legal_name, building, street, phone, permit_number, permid_expiration, day care id, url, date_permitted, actual.

```{r}
Childcare_center<-
  raw_data%>%
  janitor::clean_names() %>%
  filter(status=="Permitted")%>%
  select(-legal_name,-building,-street,-phone,-permit_number,-permit_expiration,
         -day_care_id,-url,-date_permitted,-actual)%>%
  drop_na(violation_rate_percent)%>%
  drop_na(public_health_hazard_violation_rate)

```

We investigated the severity of the presence of violation records in different types of inspections. The data graphs show that no-violation is the most frequent among the different types of inspections, and general violation is the highest among the inspections of initial annual inspection and monitoring inspection non-routine, except for no-violation. On the contrary, in the compliance inspection of open violations, critical cases are indeed more than general. lead based paint or lead in water inspection, although the number is small, we can still see that most of them are no-violation. 
```{r}
inspec_violation_summary<-
  Childcare_center%>%
select(borough,inspection_summary_result,violation_category)%>%
  mutate(violation_category = ifelse( is.na(violation_category), "NO VIOLATION", violation_category))%>%
drop_na(inspection_summary_result)%>%
  mutate(
general_category=case_when(
inspection_summary_result %like% "^Compliance Inspection of Open Violations" ~"Compliance Inspection of Open Violations",
inspection_summary_result %like% "^Initial Annual Inspection" ~"Initial Annual Inspection",
inspection_summary_result %like% "^Lead Based Paint or Lead in Water Inspection" ~"Lead Based Paint or Lead in Water Inspection",
inspection_summary_result %like% "^Monitoring Inspection Non-Routine" ~"Monitoring Inspection Non-Routine")
)%>%
  group_by(general_category,violation_category)%>%
  summarise(
    n_obs=n()
  )%>%
  ggplot(aes(fill =violation_category, x=general_category,y = n_obs))+
  geom_bar(position = "dodge", stat = "identity")+
theme(axis.text.x = element_text(size=10, angle=45, hjust = 1))+
  labs(y="number of violations",title="Inspection categories vs.violation categories",x="inspection categories")
  
ggplotly(inspec_violation_summary)


```

borough vs. inspection summary result 

We examined the inspection categories of child care centers in different areas of New York that had records of violations，We found that the categories of inspection are divided into four major categories, which are Compliance Inspection of Open Violations, Initial Annual Inspection, Lead Based Paint or Lead in Water Inspection, Monitoring Inspection Non-Routine.
```{r}
library(dplyr)
library(data.table)

borough_inspec_summmary<-
  Childcare_center%>%
  select(borough,inspection_summary_result)%>%
  drop_na(inspection_summary_result)%>%
  group_by(borough,inspection_summary_result)%>%
  summarise(
    n_obs=n()
  )%>%
  mutate(
    general_category=case_when(
      inspection_summary_result %like% "^Compliance Inspection of Open Violations" ~"Compliance Inspection of Open Violations",
      inspection_summary_result %like% "^Initial Annual Inspection" ~"Initial Annual Inspection",
      inspection_summary_result %like% "^Lead Based Paint or Lead in Water Inspection" ~"Lead Based Paint or Lead in Water Inspection",
      inspection_summary_result %like% "^Monitoring Inspection Non-Routine" ~"Monitoring Inspection Non-Routine")
  )
```
To better examine the number of violations in different types of inspections at child care centers in different borough of New York, we categorized and summarise the records of violation inspections by borough and type of inspection.

borough group by general_category
```{r}
borough_inspec_general_sumary<-
  borough_inspec_summmary%>%
  group_by(borough,general_category)%>%
  summarise(
    n_obs=sum(n_obs)
  )
borough_inspec_general_sumary
```
We also created the following chart by type of inspection and the number of violations recorded. We found that New York's child care centers had the highest number of violations in the intial annual inspection, far exceeding the other three types of violations combined, with the Queen's district having the highest number of violations at 3,600 records. In contrast, Lead Based Paint or Lead in Water Inspection had the least number of violations, with bronx having ten records, Brooklyn having eleven records, Manhattan having six records, queens having five records, and staten island not even having this type of record.

```{r}
borough_inspec_general_sumary_plot_all<-
  borough_inspec_general_sumary%>%
  ggplot(aes(x=general_category,y=n_obs),)+
  geom_bar(aes(fill = borough), stat = "identity")+
  theme(axis.text.x = element_text(size=10, angle=45, hjust = 1))+
  labs(y="number of violations",title="Inspection categories vs. borough",x="inspection categories")
  
ggplotly(borough_inspec_general_sumary_plot_all)
```

general type vs borough

```{r}
inspec_general_borough_sumary<-
borough_inspec_summmary%>%
group_by(general_category,borough)%>%
summarise(
n_obs=sum(n_obs)
)
inspec_general_borough_sumary
```

The following chart can better understand the violation situation of different Boroughs in New York. We can see that queens has the most violation records, Brooklyn has less violation records than queens but still far more than bronx and Manhattan, and staten island has the least violation records.
```{r}
violation_borough_sumary_all<-
inspec_general_borough_sumary%>%
ggplot(aes(x=borough,y=n_obs))+
geom_bar(aes(fill=general_category),stat = "identity")+
theme(axis.text.x = element_text(size=10, angle=45, hjust = 1))+
  labs(y="number of violations",title="borough vs.Inspection categories",x="borough")
  
ggplotly(violation_borough_sumary_all)
```


---------------------------------------------------------stop---------------------------------------------------------------------------
the plots below is detailed information to explore the relationship between borough and inspections (maybe for Shiny????)
```{r}
borough_inspec_general_sumary_plot_BRONX<-
  borough_inspec_general_sumary%>%
  filter(borough=="BRONX")%>%
  ggplot(aes(x=general_category,y=n_obs))+
  geom_bar(stat = "identity")+
  theme(axis.text.x = element_text(size=10, angle=45, hjust = 1))
borough_inspec_general_sumary_plot_BRONX

borough_inspec_general_sumary_plot_BROOKLYN<-
  borough_inspec_general_sumary%>%
  filter(borough=="BROOKLYN")%>%
  ggplot(aes(x=general_category,y=n_obs))+
  geom_bar(stat = "identity")+
  theme(axis.text.x = element_text(size=10, angle=45, hjust = 1))
borough_inspec_general_sumary_plot_BROOKLYN

borough_inspec_general_sumary_plot_MANHATTAN<-
  borough_inspec_general_sumary%>%
  filter(borough=="MANHATTAN")%>%
  ggplot(aes(x=general_category,y=n_obs))+
  geom_bar(stat = "identity")+
  theme(axis.text.x = element_text(size=10, angle=45, hjust = 1))
borough_inspec_general_sumary_plot_MANHATTAN

borough_inspec_general_sumary_plot_QUEENS<-
  borough_inspec_general_sumary%>%
  filter(borough=="QUEENS")%>%
  ggplot(aes(x=general_category,y=n_obs))+
  geom_bar(stat = "identity")+
  theme(axis.text.x = element_text(size=10, angle=45, hjust = 1))
borough_inspec_general_sumary_plot_QUEENS

borough_inspec_general_sumary_plot_STATENISLAND<-
  borough_inspec_general_sumary%>%
  filter(borough=="STATEN ISLAND")%>%
  ggplot(aes(x=general_category,y=n_obs))+
  geom_bar(stat = "identity")+
  theme(axis.text.x = element_text(size=10, angle=45, hjust = 1))
borough_inspec_general_sumary_plot_STATENISLAND
```

```{r}
Open_violation_borough_sumary<-
  inspec_general_borough_sumary%>%
  filter(general_category=="Compliance Inspection of Open Violations")%>%
  ggplot(aes(x=borough,y=n_obs))+
  geom_bar(stat = "identity")+
  theme(axis.text.x = element_text(size=10, angle=45, hjust = 1))
Open_violation_borough_sumary

Intial_Annual_violation_borough_sumary<-
  inspec_general_borough_sumary%>%
  filter(general_category=="Initial Annual Inspection")%>%
  ggplot(aes(x=borough,y=n_obs))+
  geom_bar(stat = "identity")+
  theme(axis.text.x = element_text(size=10, angle=45, hjust = 1))
Intial_Annual_violation_borough_sumary

Lead_violation_borough_sumary<-
  inspec_general_borough_sumary%>%
  filter(general_category=="Lead Based Paint or Lead in Water Inspection")%>%
  ggplot(aes(x=borough,y=n_obs))+
  geom_bar(stat = "identity")+
  theme(axis.text.x = element_text(size=10, angle=45, hjust = 1))
Lead_violation_borough_sumary

Non_Routine_violation_borough_sumary<-
  inspec_general_borough_sumary%>%
  filter(general_category=="Monitoring Inspection Non-Routine")%>%
  ggplot(aes(x=borough,y=n_obs))+
  geom_bar(stat = "identity")+
  theme(axis.text.x = element_text(size=10, angle=45, hjust = 1))
Non_Routine_violation_borough_sumary
```



```{r}
clean = Childcare_center %>% 
  mutate(borough = as.factor(borough), program_type = as.factor(program_type)) %>%
  group_by(borough, program_type) %>% 
  count(violation_category)

fit = lm(n~ borough + program_type, data = clean)
anova(fit) %>% 
  knitr::kable(caption = "Two way anova of violation frequency and month")
```